Drug sensitivity prediction with normal inverse Gaussian shrinkage informed by external data

### 2020-04-02 docs/manuscript1.Rnw
rewrote simulations
added simulation with noise in external covariate models

	\section{Discussion}\label{sec:discussion}
<<time>>=
# load("results/analysis_gdsc_fit1.Rdata")
# time2.semnig <- sum(fit2.semnig$time)
time2.semnig <- 1
@
	The preceding presents a novel model for drug sensitivity
	prediction from a set of high dimensional molecular features. The model allows
	for the inclusion of discrete and continuous external covariates on both the 
	drugs and features. Inclusion of the external information is through 
	data-driven and adaptive empirical Bayes estimation of the hyperparameters in 
	the normal inverse Gaussian prior model (\ref{eq:prior}). Estimation is 
	efficient and scales well with the number of features and samples.

	Estimation of the NIG model that includes both external drugs and feature
	covariates (NIG$_{\text{f}+\text{d}}$ in Section \ref{sec:gdsc}) on the GDSC
	data from Section
	\ref{sec:gdsc} took \Sexpr{round(time2.semnig, 2)} seconds on a 2016 
	MacBook Pro with a 2 GHz Dual-Core Intel Core i5 processor and
	8 GB of 1867 MHz LPDDR3 memory, running macOS  10.15.1.

@@

  The choice to model the $\bm{\alpha}$`s, as hyperparameters instead of
  full Bayesian parameters is three-fold: (i) it allows fast and stable 
  empirical Bayes estimation as compared to badly mixing (see Comment 5)
  full Bayesian MCMC sampling. (ii) \cite{wiel_learning_2019} shows that in a 
  somewhat similar model, empirical Bayes is competitive to full Bayesian 
  inference in terms of frequentist coverage of credible intervals, i.e.,
  uncertainty propagation of the hyperparameters is not always necessary.
  Additionally, (iii) in SM Section \ref{sm-sec:gibbssampler} a full Bayes
  Gibbs sampler is described, where the full conditional of the $\bm{\alpha}$ is
  Gaussian. For vague $\bm{\alpha}$ and $\lambda$ priors, the mean of this 
  Gaussian coincides 
  with the empirical Bayes updates as described in the MD, a strong 
  indication that the posterior point estimates of our EB approach and the full
  Bayes model are similar.

>>>>

	\section{Discussion}\label{sec:discussion}
<<time>>=
# load("results/analysis_gdsc_fit1.Rdata")
# time2.semnig <- sum(fit2.semnig$time)
time2.semnig <- 1
@
	The preceding presents a novel model for drug sensitivity
	prediction from a set of high dimensional molecular features. The model allows
	for the inclusion of discrete and continuous external covariates on both the 
	drugs and features. Inclusion of the external information is through 
	data-driven and adaptive empirical Bayes estimation of the hyperparameters in 
	the normal inverse Gaussian prior model (\ref{eq:prior}). Estimation is 
	efficient and scales well with the number of features and samples.
	Estimation of the NIG model that includes both external drugs and feature
	covariates (NIG$_{\text{f}+\text{d}}$ in Section \ref{sec:gdsc}) on the GDSC
	data from Section
	\ref{sec:gdsc} took \Sexpr{round(time2.semnig, 2)} seconds on a 2016 
	MacBook Pro with a 2 GHz Dual-Core Intel Core i5 processor and
	8 GB of 1867 MHz LPDDR3 memory, running macOS  10.15.1.

@@

  Another possible criticism is the treatment of $\bm{\alpha}$ as fixed
  hyperparameters instead of random. A Bayesian could argue that endowment of 
  $\bm{\alpha}$ with a hyperprior results in propagation of 
  uncertainty about $\bm{\alpha}$ and as a result improved regression parameter 
  uncertainty quantification. \cite{wiel_learning_2019} show in a similar 
  setting that EB estimation of hyperparameters does not necessarily lead to
  worse uncertainty quantification as measured by frequentist coverage of
  Bayesian credible intervals, as compared to a full Bayes treatment of the
  hyperparameters.
